\newpage
\section{Memorandum}


\noindent To: The Global Professional Tennis Coach Association (GPTCA)

\noindent From: Team \#2416613 

\noindent Subject:  The Role of Momentum in Tennis Movement

\noindent Date: February 5, 2024 
\\

 \noindent Dear Officer of GPTCA:

From the model established by our team based on match data, we have found that Momentum plays a crucial role in tennis matches. Evaluating the Momentum indicator through model parameters in multiple matches for the same player allows for a high probability prediction of the score trend in subsequent matches. Furthermore, after neutralizing the skill gap between opposing players, the Momentum between different players in the same match shows a positive correlation with their performance.

Analyzing the predictive effects and understanding the changes in momentum, we have several important findings and suggestions that we hope will help improve the accuracy of your decisions.

\begin{enumerate}
\item Place special emphasis on the initial momentum shifts of both the opponent and one's own team during the match. Through the analysis presented earlier, it was observed that the momentum at the beginning of the game has a significant impact on the overall match. However, it is equally important to acknowledge the potential threat posed by momentum shifts resulting from underestimating the opponent.

\item In terms of model predictions, the undeniable improvement in accuracy of the MM-LSTM model compared to the fitted traditional models serves as compelling evidence for the powerful influence of momentum.

\item  For certain decisive factors, such as unstoppable winning serves or serving errors, their impact on momentum is significant and can influence players' attempts to build on success or stage a comeback during the match.
\end{enumerate}

Additionally, here are recommendations for players dealing with unexpected and decisive events in the flow of a tennis match:
\begin{enumerate}
\item  It's essential to break free from negative thinking early on and mentally fortify oneself like a warrior. Pay no mind to the opponent and strive to exhibit strength and resilience.

\item  Choosing the right moment to ignite one's inner passion undoubtedly proves more beneficial in the competition. Avoid expending energy too early and learn to manage time and energy wisely.

\item  During practice, keep score, so you can forget about the score during the match. In data analysis, it is evident that previous historical scores have a significant impact on the current situation. 
\end{enumerate}

In conclusion, in a match, robust physique, a stable and healthy mindset, appropriate strategic planning, and exceptional technical skills are all indispensable.

\begin{flushright}
    \textbf{Yours Sincerely,} \\
    \textbf{Team \#2416613}
\end{flushright}
